---
title: "CPLN 6890 Data Store"
author: "Michael Fichman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(mapview)
library(kableExtra)
```

# About

This page consolidates data links and sources for students in CPLN 6890 - The City at Night - at the University of Pennsylvania's Weitzman School of Design, Department of City and Regional Planning.

During the Fall semester of 2025, students will undertake nighttime Area Studies of five Philadelphia sites. Part of this process will involve data analysis of relevant information - public safety incidents, zoning, business licenses, and more.

Many useful data sources are consolidated on this site for ease of access.

# Map of Area Study Sites

The following map shows the five study areas.

You can grab spatial data delineating the boundaries of the study areas as shp (in a zipfile), or as geojson in the "study_areas" folder in the [class GitHub Repo](https://github.com/mafichman/cpln_6890/tree/main/study_areas/2025).


```{r}
study_areas <- st_read("https://raw.githubusercontent.com/mafichman/cpln_6890/refs/heads/main/study_areas/2025/geojson/study_areas_2025.geojson")

mapview(study_areas, label = study_areas$Name)

```

The following sections are under construction, and will be filled with relevant data sets for Area Study #2.

# Land Use

[City of Philadelphia Zoning](https://opendataphilly.org/datasets/zoning-base-districts/)

[City of Philadelphia Zoning Overlays](https://opendataphilly.org/datasets/zoning-overlays/)

[City of Philadelphia Special Vending Districts](https://opendataphilly.org/datasets/special-vending-districts/)

You can consult [Section 14-602 of the Philadelphia Code](https://codelibrary.amlegal.com/codes/philadelphia/latest/philadelphia_pa/0-0-0-292339) to understand what kinds of uses are prohibited in each zoning district.

# Licensing

[PA Liquor Control Board Licenses - Philadelphia County](https://github.com/mafichman/cpln_6890/blob/main/plcb_licenses/PHL_PLCB_geocoded.csv)

[City of Philadelphia Business Activity Licenses](https://opendataphilly.org/datasets/licenses-and-inspections-business-licenses/)

# OSM code

Under construction

# Public Safety

[Philadelphia Police Department Crime incidents](https://opendataphilly.org/datasets/crime-incidents/)

[City of Philadelphia Licenses and Inspections - Code Violations and Permit Refusals](https://opendataphilly.org/datasets/licenses-and-inspections-appeals-of-code-violations-and-permit-refusals/)

311

# Mobility And Transportation

Under construction - 8010 2021 project

IndiGo

SETPA

# Political Boundaries

Police Districts

Council Districts

Registered Community Organizations

Commercial Corridor Boundaries